Are you moving predictably?

### 2018-07-11 dokumentation/submission.tex
fertig
added small introduction to neural nets

	\subsection{Classification} \label{subsec: classification}
	%TODO: clustering
	%TODO (5 pages)	
	{}\input{MiriamClustering}

	\input{DecisionTree}
	%\subsection{Neural Net}
	%TODO (5 pages)	
	\subsection{Neural Net} \label{subsec: neural net}
	For all the neural net computations we considered person vector data sets of different sizes (c.f. \Cref{subsec: person vector data}).\\

@@

	\subsection{People living over/under standards}
	%TODO

>>>>

	\subsection{Classification} \label{subsec: classification}
	%TODO: clustering
	%TODO (5 pages)	
	\input{MiriamClustering}

	\input{DecisionTree}
	%\subsection{Neural Net}
	%TODO (5 pages)	
	\subsection{Neural Net} \label{subsec: neural net}
	In this section we want to further improve the accuracy of predicting the strata of one person by using neural networks. Like in the previous section, when we used decision trees, we need ground truth, in this case the strata, to be able to train the neural networks. For all the neural net computations we considered person vector data sets of different sizes (c.f. \Cref{subsec: person vector data}).\\

@@

	\subsection{People living over/under standards}
	There are a lot of people spending more or less money than they actually have. So for example there are people not earning a lot of money, but still having a car. Or people earning a lot, but spend it just on holidays or never for bad times.
